Precise predictions for same-sign W-boson scattering at the LHC

### 2018-03-08 Draft/shower.tex

We now discuss how different predictions compare when the matching to parton shower is included. For such
a comparison we expect larger discrepancy than what we found at fixed-order, as a consequence of the different
matching schemes, parton shower employed, and of other details of the matching (such as the choice of the parton shower initial scale). Among
the codes capable of providing fixed-order results, presented before, {\sc MG5\_aMC}, the {\sc Powheg-Box}, and {\sc VBFNLO}
can also provide results at (N)LO+PS accuracy. For {\sc VBFNLO} matched to {\sc Herwig} and the {\sc Powheg-Box}, we
restrict ourselves to showing results only in the VBS approximation,
{\emph i.e.}\ the $s$-channel contributions are neglected here. Besides,
also {\sc PHANTOM} and {\sc WHIZARD} are used for LO+PS results.\\
{\sc MG5\_aMC}, which
employs the {\sc MC@NLO}~\cite{Frixione:2002ik} matching procedure, will be used together with {\sc Pythia8}~\cite{Sjostrand:2014zea} (version 8.223)
and {\sc Herwig++}~\cite{Bahr:2008pv, Bellm:2013hwb} (version 2.7.1). The same parton showers will be employed for the LO results of {\sc PHANTOM} and {\sc Pythia8} will also be employed for the LO results of {\sc WHIZARD}. For the {\sc Powheg-Box}, the namesake
matching procedure is employed~\cite{Nason:2004rx,Frixione:2007vw}, together with {\sc Pythia8} (version 8.230). {\sc VBFNLO} serves as a matrix-element and phase-space provider
for the {\sc Matchbox} module~\cite{Platzer:2011bc} of {\sc
Herwig7}~\cite{Bellm:2015jjp,Bellm:2017bvx}, using an extended version of the BLHA
interface~\cite{Binoth:2010xt,Alioli:2013nda,Andersen:2014efa}. The {\sc Matchbox} module makes it
possible to choose between {\sc MC\-@NLO}-like and {\sc Powheg}-like
matching. As parton shower, both the default angular-ordered shower as
well as the dipole shower can be employed.\ZM{Which matching scheme is used here in VBFNLO?}
Whenever {\sc Pythia8}\ is used, the Monash tune~\cite{Skands:2014pea} is selected. Multiple-parton interactions are disabled.

@@

Compared to the fixed order computations, a slightly different set-up has been employed for {\sc MG5\_aMC} in order to simplify the calculation: instead of generating the full
${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process, since it is dominated by doubly-resonant contribution, the
events are produced for the process with two stable ${\rm W}^+$-bosons (${\rm p}{\rm p}\to{\rm W^+}{\rm W^+}{\rm j}{\rm j}$), and the decay of these ${\rm W}^+$-bosons
is simulated with {\sc MadSpin}~\cite{Artoisenet:2012st} (ensuring spin correlations) before the PS. Since {\sc MadSpin}\ computes
the partial and total decay width of the W bosons at LO accuracy only, while in Section~\ref{subsec:inputpar} the NLO width is employed,
an effect ($6\%$) on the normalisation is induced.

@@

We now present the results of predictions matched to parton shower.
The total rates within VBS cuts are displayed in Tables~\ref{tab:PSratesLO} and
\ref{tab:PSratesNLO}, at LO and NLO
accuracy respectively. For {\sc MG5\_aMC},
the numbers with $\Gamma_{\rm resc}$ are rescaled to
take into account the width effects described in the above paragraph. At NLO accuracy, for {\sc MG5\_aMC} + {\sc Pythia8} and {\sc VBFNLO}-{\sc Dipole}, we also quote
theoretical uncertainties.
For the former, we show both PDF and scale uncertainties,\footnote{A preliminary study on PDF uncertainties in VBS has appeared
in Ref.~\cite{Schwan:2017yy}.} obtained via exact reweighting~\cite{Frederix:2011ss} by varying independently the renormalisation and factorization
scale by a factor of two around its central value, Eq.~(\ref{eq:defscale}) (nine-point variations).
For the latter, we show the
three-point scale uncertainties, obtained by considering correlated variations of the renormalisation and factorisation scales. Theory uncertainties should have very little dependence on the tool employed.
We observe that, once the width effect is taken into
account, total rates from different tools agree within a few per cent, both at LO and NLO. Larger discrepancies, however, will appear for differential observables, which we are going to discuss in
the following. Theory uncertainties on the total rates are very small, regardless of whether scale variations are estimated with 
independent or correlated variations of the renormalisation and factorisation scales.
Concerning differential distributions, for each observable we will display results in two plots, shown side-by-side. In the plot on the left (right), (N)LO+PS predictions are shown
with different colours in the main frame. In the inset, these predictions are compared in both cases with a fixed-order prediction at NLO accuracy (obtained with
{\sc VBFNLO}, \emph{i.e.}\ the VBS approximation with $s$-channel).
For the differential observables, the {\sc MG5\_aMC} predictions are \emph{not} rescaled to compensate for the width effect mentioned above. As for the table, we show theoretical uncertainties for the NLO+PS samples
obtained with {\sc VBFNLO} and {\sc MG5\_aMC}:
again, for the first the band corresponds to three-point variations, while for the second the darker (lighter) band corresponds to nine-point
scale variations (plus PDF uncertainties, linearly added).

@@

\begin{figure*}[hbt]
\centering
\includegraphics[width=0.47\textwidth]{figures/LOPS/jetsexclusive.pdf}
\includegraphics[width=0.47\textwidth]{figures/NLOPS/jetsexclusive.pdf}
\caption{Differential distribution in the
exclusive jet multiplicity
from predictions matched to parton shower, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
    {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for {\sc MG5\_aMC}+{\sc Pythia8} the darker and lighter bands correspond
    respectively to the nine-point scale uncertainty and the scale and PDF uncertainties combined linearly.
    The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.}
\label{fig:PSnjet}
\end{figure*}

\begin{figure*}[hbt]
\centering
\includegraphics[width=0.47\textwidth]{figures/LOPS/m_jj.pdf}
\includegraphics[width=0.47\textwidth]{figures/NLOPS/m_jj.pdf}
\caption{Differential distribution in the
invariant mass of the two tagging jets
from predictions matched to parton shower, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
    {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for {\sc MG5\_aMC}+{\sc Pythia8} the darker and lighter bands correspond
    respectively to the nine-point scale uncertainty and the scale and PDF uncertainties combined linearly.
    The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.}
\label{fig:PSmjj}
\end{figure*}

@@

The transverse momentum of the hardest and second-hardest jets are shown in Figs.~\ref{fig:PSpt1} and~\ref{fig:PSpt2}, respectively. In general, for both observables,
predictions from different tools agree rather well with each other, with a spread at most at the 10\% level. At LO+PS, typically the transverse-momentum spectra are softer than
the fixed-NLO ones, and this effect is more marked for the second-hardest jet which, as expected, is more sensitive to the description of the extra radiation. Again, this
effect is mitigated by NLO corrections. The only feature that may be worth noticing among the NLO+PS predictions is the tendency of the {\sc Powheg-Box} to suppress the
hardest-jet spectrum at low transverse momentum ($\ptsub{\Pj_1}<100 \GeV$).\\
If we consider the rapidity of the second jet, Fig.~\ref{fig:PSy2}, we observe again rather small differences among tools, with the tendency towards a general
stabilisation at NLO+PS. However, some (small) differences in the shape remain at NLO+PS, which are worth to be briefly discussed: predictions
obtained with {\sc MG5\_aMC} are very close to the fixed-order prediction; the {\sc Powheg-Box}\ displays an enhancement of the central region, and a consequent suppression in the
peripheral region, while {\sc VBFNLO} shows an opposite behaviour. However, the effect is rather small, with the largest departure from the fixed-order prediction being
at most $10\%$.\footnote{If the setting {\tt SpaceShower:dipole\-Recoil = on} (discussed in the following)
is used when {\sc Pythia8}\ is employed together with the {\sc Powheg-Box}, the enhancement at central rapidities and the depletion
at small value of transverse momentum are partially compensated.}

@@

\begin{figure*}[hbt]
\centering
\includegraphics[width=0.47\textwidth]{figures/LOPS/Deltay_jj.pdf}
\includegraphics[width=0.47\textwidth]{figures/NLOPS/Deltay_jj.pdf}
\caption{Differential distribution in the
rapidity separation of the two tagging jets
from predictions matched to parton shower, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
    {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for {\sc MG5\_aMC}+{\sc Pythia8} the darker and lighter bands correspond
    respectively to the nine-point scale uncertainty and the scale and PDF uncertainties combined linearly.
    The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.}
\label{fig:PSdyjj}
\end{figure*}

\begin{figure*}[hbt]
\centering
\includegraphics[width=0.47\textwidth]{figures/LOPS/pT_j1.pdf}
\includegraphics[width=0.47\textwidth]{figures/NLOPS/pT_j1.pdf}
\caption{Differential distribution in the
transverse momentum of the hardest jet
from predictions matched to parton shower, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
    {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for {\sc MG5\_aMC}+{\sc Pythia8} the darker and lighter bands correspond
    respectively to the nine-point scale uncertainty and the scale and PDF uncertainties combined linearly.
    The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.}
\label{fig:PSpt1}
\end{figure*}

\begin{figure*}[hbt]
\centering
\includegraphics[width=0.47\textwidth]{figures/LOPS/pT_j2.pdf}
\includegraphics[width=0.47\textwidth]{figures/NLOPS/pT_j2.pdf}
\caption{Differential distribution in the
transverse momentum of the second-hardest jet
from predictions matched to parton shower, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
    {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for {\sc MG5\_aMC}+{\sc Pythia8} the darker and lighter bands correspond
    respectively to the nine-point scale uncertainty and the scale and PDF uncertainties combined linearly.
    The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.}
\label{fig:PSpt2}
\end{figure*}

\begin{figure*}[hbt]
\centering
\includegraphics[width=0.47\textwidth]{figures/LOPS/y_j2.pdf}
\includegraphics[width=0.47\textwidth]{figures/NLOPS/y_j2.pdf}
\caption{Differential distribution in the
rapidity of the second-hardest jet
from predictions matched to parton shower, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
    {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for {\sc MG5\_aMC}+{\sc Pythia8} the darker and lighter bands correspond
    respectively to the nine-point scale uncertainty and the scale and PDF uncertainties combined linearly.
    The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.}
\label{fig:PSy2}
\end{figure*}

\begin{figure*}[hbt]
\centering
\includegraphics[width=0.47\textwidth]{figures/LOPS/z_j3.pdf}
\includegraphics[width=0.47\textwidth]{figures/NLOPS/z_j3.pdf}
\caption{Differential distribution in the
Zeppenfeld variable of the third-hardest jet
from predictions matched to parton shower, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
    {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for {\sc MG5\_aMC}+{\sc Pythia8} the darker and lighter bands correspond
    respectively to the nine-point scale uncertainty and the scale and PDF uncertainties combined linearly.
    The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.}
\label{fig:PSz3}
\end{figure*}

>>>>

We now discuss how different predictions compare when the matching to parton shower is included. For such
a comparison we expect larger discrepancy than what we found at fixed-order, as a consequence of the different
matching schemes, parton shower employed, and of other details of the matching (such as the choice of the parton shower initial scale). Among
the codes capable of providing fixed-order results, presented before, {\sc MG5\_aMC}, the {\sc Powheg-Box}, and {\sc VBFNLO}
can also provide results at (N)LO+PS accuracy. For {\sc VBFNLO} matched to {\sc Herwig} and the {\sc Powheg-Box}, we
restrict ourselves to show results only in the VBS approximation,
{\emph i.e.}\ the $s$-channel contributions are neglected here. Besides,
also {\sc PHANTOM} and {\sc WHIZARD} are used for LO+PS results.\\
{\sc MG5\_aMC}, which
employs the {\sc MC@NLO}~\cite{Frixione:2002ik} matching procedure, will be used together with {\sc Pythia8}~\cite{Sjostrand:2014zea} (version 8.223)
and {\sc Herwig++}~\cite{Bahr:2008pv, Bellm:2013hwb} (version 2.7.1). The same parton showers will be employed for the LO results of {\sc PHANTOM} and {\sc Pythia8} will also be employed for the LO results of {\sc WHIZARD}. For the {\sc Powheg-Box}, the namesake
matching procedure is employed~\cite{Nason:2004rx,Frixione:2007vw}, together with {\sc Pythia8} (version 8.230). {\sc VBFNLO} serves as a matrix-element and phase-space provider
for the {\sc Matchbox} module~\cite{Platzer:2011bc} of {\sc
Herwig7}~\cite{Bellm:2015jjp,Bellm:2017bvx}, using an extended version of the Binoth Les Houcehs Accord
interface~\cite{Binoth:2010xt,Alioli:2013nda,Andersen:2014efa}. The {\sc Matchbox} module makes it
possible to choose between {\sc MC\-@NLO}-like and {\sc Powheg}-like
matching. As parton shower, both the default angular-ordered shower as
well as the dipole shower can be employed.\ZM{Which matching scheme is used here in VBFNLO?}
Whenever {\sc Pythia8}\ is used, the Monash tune~\cite{Skands:2014pea} is selected. Multiple-parton interactions are disabled.

@@

Compared to the fixed order computations, a slightly different set-up has been employed for {\sc MG5\_aMC} in order to simplify the calculation: instead of generating the full
${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process, since it is dominated by doubly-resonant contribution, the
events are produced for the process with two stable ${\rm W}^+$-bosons (${\rm p}{\rm p}\to{\rm W^+}{\rm W^+}{\rm j}{\rm j}$), and the decay of these ${\rm W}^+$-bosons
is simulated with {\sc MadSpin}~\cite{Artoisenet:2012st} (ensuring spin correlations) before the PS. Since {\sc MadSpin}\ computes
the partial and total decay widths of the W bosons at LO accuracy only, while in Section~\ref{subsec:inputpar} the NLO width is employed,
an effect ($6\%$) on the normalisation is induced.

@@

We now present the results of predictions matched to parton shower.
The total rates within VBS cuts are displayed in Tables~\ref{tab:PSratesLO} and
\ref{tab:PSratesNLO}, at LO and NLO
accuracy respectively. For {\sc MG5\_aMC},
the numbers with $\Gamma_{\rm resc}$ are rescaled to
take into account the width effects described in the above paragraph. At NLO accuracy, for {\sc MG5\_aMC} + {\sc Pythia8} and {\sc VBFNLO}-{\sc Dipole}, we also quote
theoretical uncertainties.
For the former, we show both PDF and scale uncertainties,\footnote{A preliminary study on PDF uncertainties in VBS has appeared
in Ref.~\cite{Schwan:2017yy}.} obtained via exact reweighting~\cite{Frederix:2011ss} by varying independently the renormalisation and factorisation
scales by a factor of two around the central value, Eq.~(\ref{eq:defscale}) (nine-point variations).
For the latter, we show the
three-point scale uncertainties, obtained by considering correlated variations of the renormalisation and factorisation scales. Theory uncertainties should have very little dependence on the tool employed.
We observe that, once the width effect is taken into
account, total rates from different tools agree within a few per cents, both at LO and NLO. Larger discrepancies, however, will appear for differential observables, which we are going to discuss in
the following. Theory uncertainties on the total rates are very small, regardless of whether scale variations are estimated with 
independent or correlated variations of the renormalisation and factorisation scales.
Concerning differential distributions, for each observable we will display results in two plots, shown side-by-side. In the plot on the left (right), (N)LO+PS predictions are shown
with different colours in the main frame. In the inset, these predictions are compared in both cases with a fixed-order prediction at NLO accuracy (obtained with
{\sc VBFNLO}, \emph{i.e.}\ the VBS approximation with $s$-channel).
For the differential observables, the {\sc MG5\_aMC} predictions are \emph{not} rescaled to compensate for the width effect mentioned above. As for the table, we show theoretical uncertainties for the NLO+PS samples
obtained with {\sc VBFNLO} and {\sc MG5\_aMC}:
again, for the first the band corresponds to three-point variations, while for the second the darker (lighter) band corresponds to nine-point
scale variations (plus PDF uncertainties, linearly added).

@@

\begin{figure*}[hbt]
\centering
\includegraphics[width=0.47\textwidth]{figures/LOPS/jetsexclusive.pdf}
\includegraphics[width=0.47\textwidth]{figures/NLOPS/jetsexclusive.pdf}
\caption{Differential distribution in the
exclusive jet multiplicity
from predictions matched to parton showers, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
    {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for {\sc MG5\_aMC}+{\sc Pythia8} the darker and lighter bands correspond
    respectively to the nine-point scale uncertainty and the scale and PDF uncertainties combined linearly.
    The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.}
\label{fig:PSnjet}
\end{figure*}

\begin{figure*}[hbt]
\centering
\includegraphics[width=0.47\textwidth]{figures/LOPS/m_jj.pdf}
\includegraphics[width=0.47\textwidth]{figures/NLOPS/m_jj.pdf}
\caption{Differential distribution in the
invariant mass of the two tagging jets
from predictions matched to parton showers, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
    {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for {\sc MG5\_aMC}+{\sc Pythia8} the darker and lighter bands correspond
    respectively to the nine-point scale uncertainty and the scale and PDF uncertainties combined linearly.
    The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.}
\label{fig:PSmjj}
\end{figure*}

@@

The transverse momentum of the hardest and second-hardest jets are shown in Figs.~\ref{fig:PSpt1} and~\ref{fig:PSpt2}, respectively. In general, for both observables,
predictions from different tools agree rather well with each other, with a spread at most at the 10\% level. At LO+PS, typically the transverse-momentum spectra are softer than
the fixed-NLO ones, and this effect is more marked for the second-hardest jet which, as expected, is more sensitive to the description of the extra radiation. Again, this
effect is mitigated by NLO corrections. The only feature that may be worth noticing among the NLO+PS predictions is the tendency of the {\sc Powheg-Box} to suppress the
hardest-jet spectrum at low transverse momentum ($\ptsub{\Pj_1}<100 \GeV$).

If we consider the rapidity of the second jet, Fig.~\ref{fig:PSy2}, we observe again rather small differences among tools, with the tendency towards a general
stabilisation at NLO+PS. However, some (small) differences in the shape remain at NLO+PS, which are worth to be briefly discussed: predictions
obtained with {\sc MG5\_aMC} are very close to the fixed-order prediction; the {\sc Powheg-Box}\ displays an enhancement of the central region, and a consequent suppression in the
peripheral region, while {\sc VBFNLO} shows an opposite behaviour. However, the effect is rather small, with the largest departure from the fixed-order prediction being
at most $10\%$.\footnote{If the setting {\tt SpaceShower:dipole\-Recoil = on} (discussed in the following)
is used when {\sc Pythia8}\ is employed together with the {\sc Powheg-Box}, the enhancement at central rapidities and the depletion
at small value of transverse momentum are partially compensated.}

@@

\begin{figure*}[hbt]
\centering
\includegraphics[width=0.47\textwidth]{figures/LOPS/Deltay_jj.pdf}
\includegraphics[width=0.47\textwidth]{figures/NLOPS/Deltay_jj.pdf}
\caption{Differential distribution in the
rapidity separation of the two tagging jets
from predictions matched to parton showers, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
    {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for {\sc MG5\_aMC}+{\sc Pythia8} the darker and lighter bands correspond
    respectively to the nine-point scale uncertainty and the scale and PDF uncertainties combined linearly.
    The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.}
\label{fig:PSdyjj}
\end{figure*}

\begin{figure*}[hbt]
\centering
\includegraphics[width=0.47\textwidth]{figures/LOPS/pT_j1.pdf}
\includegraphics[width=0.47\textwidth]{figures/NLOPS/pT_j1.pdf}
\caption{Differential distribution in the
transverse momentum of the hardest jet
from predictions matched to parton showers, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
    {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for {\sc MG5\_aMC}+{\sc Pythia8} the darker and lighter bands correspond
    respectively to the nine-point scale uncertainty and the scale and PDF uncertainties combined linearly.
    The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.}
\label{fig:PSpt1}
\end{figure*}

\begin{figure*}[hbt]
\centering
\includegraphics[width=0.47\textwidth]{figures/LOPS/pT_j2.pdf}
\includegraphics[width=0.47\textwidth]{figures/NLOPS/pT_j2.pdf}
\caption{Differential distribution in the
transverse momentum of the second-hardest jet
from predictions matched to parton showers, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
    {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for {\sc MG5\_aMC}+{\sc Pythia8} the darker and lighter bands correspond
    respectively to the nine-point scale uncertainty and the scale and PDF uncertainties combined linearly.
    The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.}
\label{fig:PSpt2}
\end{figure*}

\begin{figure*}[hbt]
\centering
\includegraphics[width=0.47\textwidth]{figures/LOPS/y_j2.pdf}
\includegraphics[width=0.47\textwidth]{figures/NLOPS/y_j2.pdf}
\caption{Differential distribution in the
rapidity of the second-hardest jet
from predictions matched to parton showers, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
    {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for {\sc MG5\_aMC}+{\sc Pythia8} the darker and lighter bands correspond
    respectively to the nine-point scale uncertainty and the scale and PDF uncertainties combined linearly.
    The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.}
\label{fig:PSy2}
\end{figure*}

\begin{figure*}[hbt]
\centering
\includegraphics[width=0.47\textwidth]{figures/LOPS/z_j3.pdf}
\includegraphics[width=0.47\textwidth]{figures/NLOPS/z_j3.pdf}
\caption{Differential distribution in the
Zeppenfeld variable of the third-hardest jet
from predictions matched to parton showers, at LO (left) or NLO (right) accuracy (upper plot), compared with the fixed-NLO result computed with {\sc VBFNLO} (lower plot). At NLO+PS accuracy, for
    {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties are shown, while for {\sc MG5\_aMC}+{\sc Pythia8} the darker and lighter bands correspond
    respectively to the nine-point scale uncertainty and the scale and PDF uncertainties combined linearly.
    The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.}
\label{fig:PSz3}
\end{figure*}
